### 2024-05-16 tex/gl_sankey.tex
update aq (sans font in gl)
Update w/ MAR values and Antarctic (all/E/W)
Adjust sublimation label position

    \sankeynode{name=SF, quantity=\Q{SF}, at={[xshift=0, yshift=3cm]GROSS-from-SF.center}, align=center}
    \sankeynode{name=DP, quantity=\Q{DP}, at={[xshift=-3mm, yshift=0]SF.right}, align=left}
    \sankeynode{name=CD, quantity=\Q{CD}, at={[xshift=-3mm, yshift=0]DP.right}, align=left}
    \sankeynode{name=RF-NET, quantity=\Q{RF}+\Q{RF-LIQ}, at={[xshift=-6mm, yshift=0]CD.right}, align=left}
    \sankeystart[water]{RF-NET}
    %% \sankeyadvance[water]{RF-NET}{0.5cm}

@@

    \sankeyset{ice}
    \sankeynode{ name=ML, quantity=\Q{FRET}+\Q{IL}, at={[xshift=8mm]SF.left}, anchor=right}
    \sankeystart[red]{ML}
    \sankeyadvance[red-to-ice]{ML}{1cm}
    \sankeyfork{ML}{\Q{FRET}/FRET, \Q{IL}/IL}
    \sankeydubins[minimum radius=2mm]{IL}{GROSS-from-IL}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{30}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{-30}
    \sankeyadvance{FRET}{3cm}
    %% \sankeydubins{FRET}{FRET-DYN}
    \sankeydubins{FRET}{DYN-FRET-attach}

@@

    \node[anchor=center, align=center, shift=({0cm,-1cm})] at (SU-out.center) {Sublimation\\(\sankeygetnodeqty{SU-out})};

>>>>

    \sankeynode{name=SF, quantity=\Q{SF}, at={[xshift=0, yshift=5cm]GROSS-from-SF.center}, align=center}
    \sankeynode{name=DP, quantity=\Q{DP}, at={[xshift=-3mm, yshift=0]SF.right}, align=left}
    \sankeynode{name=CD, quantity=\Q{CD}, at={[xshift=-3mm, yshift=0]DP.right}, align=left}
    \sankeynode{name=RF-NET, quantity=\Q{RF}+\Q{RF-LIQ}, at={[xshift=-6mm, yshift=0]CD.right}, align=left}
    \sankeystart[water]{RF-NET}
    %% \sankeyadvance[water]{RF-NET}{0.5cm}

@@

    \sankeyset{ice}
    \sankeynode{ name=ML, quantity=\Q{FRET}+\Q{IL}, at={[xshift=8mm]SF.left}, anchor=right}
    \sankeystart[red]{ML}
    %% \sankeynode{ name=ML_start, quantity=\Q{FRET}+\Q{IL}, at={[xshift=8mm]SF.left}, 
      anchor=left, angle=90}
    %% \sankeyend[red]{ML_start}
    \sankeyadvance[red-to-ice]{ML}{1cm}
    \sankeyfork{ML}{\Q{FRET}/FRET, \Q{IL}/IL}
    \sankeydubins[minimum radius=2mm]{IL}{GROSS-from-IL}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{30}
    \sankeyadvance{FRET}{2cm}
    \sankeyturnleft{FRET}{-30}
    \sankeyadvance{FRET}{3cm}
    %% \sankeydubins{FRET}{FRET-DYN}
    \sankeydubins{FRET}{DYN-FRET-attach}

@@

    \node[anchor=center, align=center, shift=({0cm,1cm})] at (SU-out.center) {Sublimation\\(\sankeygetnodeqty{SU-out})};
